Higher order unification for free!

### 2024-04-09 paper/main.tex
rephrase of some sentences

\paragraph{Decompilation}
Decompilation of \linketa is performed by adding new rules to the
\elpiIn{commit-link} predicate. In particular, given \linketaM{\Gamma}{X}{t}, we
can note that this unification never fails, since $X$ is a flexible term and no
other \linketa has $X$ has \lhs (by \cref{def:progressetadedup}). The link is
remove from \linkStore and \elpiIn{commit-links} terminates.

@@

\noteD[inline]{Below the proof of \cref{prop:nf}, ho usato 3 lemmi ausiliari,
forse si può compattare in una prova più piccola?}
\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

\begin{proof}[Proof sketch]
  Let $\sigma$ be the substitution, such that $\wellb(\sigma)$. $\lhs \in
  \sigma$, therefore $\wellb(\lhs)$. By \cref{def:progressetaleft}, if 1) \lhs is
  a name, a constant of an application, then, \lhs is unified with the
  $\eta$-reduced term $t$ obtain from \rhs. By \cref{cor:rhs-eta-onelamb}, \rhs
  has one lambda, therefore $\wellb(t)$. Otherwise, 2) \lhs has \elpiIn{lam} as
  functor, \rhs should not be an $\eta$-expansion ans, so, $\wellb(\rhs)$. In
  both cases, unification is performed between terms in \wellb.
\end{proof}

>>>>

\paragraph{Decompilation}
Decompilation of the remaining \linketa (i.e. the \linketa that have been
activated) is performed by iterating over them and unifying \lhs and \rhs. Note
that this unification never fails, since \lhs is a flexible term not appearing
in any other \linketa (by \cref{def:progressetadedup}).

@@

% \noteD[inline]{Below the proof of \cref{prop:nf}, ho usato 3 lemmi ausiliari,
% forse si può compattare in una prova più piccola?}
\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaleft is between
  terms in $\wellb$  
  \label{lemma:unif-eta-1}
\end{lemma}

\begin{proof}[Proof sketch]
  Let $\sigma$ be the substitution, which is  $\wellb(\sigma)$ (by
  \cref{prop:nf}). $\lhs \in \sigma$, therefore $\wellb(\lhs)$. By
  \cref{def:progressetaleft}, if 1) \lhs is a name, a constant of an
  application, then, $\lambda x.\lhs \appsep x$ is unified with \rhs. By
  \cref{inv:link-eta-right}, $\rhs = \lambda x. t$, therefore $\wellb(t)$.
  Otherwise, 2) \lhs has \elpiIn{lam} as functor, \rhs should not be an
  $\eta$-expansion, so, $\wellb(\rhs)$. In both cases, unification is
  performed between terms in \wellb.
\end{proof}
